Space is the Place: How Dispersal and Competition Shape Genetic Variation in Continuous Space

### 2018-11-20 ms/spaceness.tex
updated title
misc

\title{ Evolution on the Final Frontier: How Dispersal and Competition Shape Genetic Variation in Continuous Space }
\author{C. J. Battey, Peter Ralph, Andrew Kern}
\date{November 2018} % delete this line to display the current date

@@

\section{Abstract}
Random mating is a core assumption of many population genetic models, but likely occurs in few real populations. Instead most organisms mate with nearby individuals and disperse across only a small part of the full range of a species. This process creates the pattern known as isolation by distance (IBD; Wright 1942) -- a positive correlation between genetic and geographic distances among individuals. Though this pattern is both expected from first principles and widely observed in natural populations (Aguillon et al. 2017, Pinto et al. 2013, Battey et al. 2018), existing population genetic models either exclude it entirely (by assuming random mating) or take the heuristic approach of binning the landscape into discrete blocks of randomly mating populations that exchange migrants each generation.

@@

\section{Introduction}

>>>>

\title{ Space is the Place: How Dispersal and Competition Shape Genetic Variation in Continuous Space }
\author{C. J. Battey, Peter Ralph, Andrew Kern}
\date{November 2018} % delete this line to display the current date

@@

\section{Abstract}

\section{Introduction}
Random mating is a core assumption of many population genetic models, but likely occurs in few real populations. Instead most organisms mate with nearby individuals and disperse across only a small part of the full range of a species. This process creates the pattern known as isolation by distance (IBD; Wright 1942) -- a positive correlation between genetic and geographic distances among individuals. Though this pattern is both expected from first principles and widely observed in natural populations (Aguillon et al. 2017, Pinto et al. 2013, Battey et al. 2018), existing population genetic models either exclude it entirely (by assuming random mating) or take the heuristic approach of binning the landscape into discrete blocks of randomly mating populations that exchange migrants each generation.

@@
